Data Hygiene Gotchas

### 2016-09-16 articles/data_hygiene/data_hygiene.Rmd
fix typos

Sometimes, missing category values can convery important messages. A classific example is someone who is applying for loans and they non-reported their income category. Or maybe it shoudln't be missing and it's just something wrong with our data sources (e.g. database, or the way we're querying it).

>>>>

Sometimes, missing category values can convey important messages. A classific example is someone who is applying for loans and they non-reported their income category. Or maybe it shouldn't be missing and it's just something wrong with our data sources (e.g. database, or the way we're querying it).
